\tophead{Preparing Documentation for this system}

This system uses latex2html to prepare the web pages, and pdflatex
to prepare the PDF files, and SVN (Sub Version system) to archive
the original documents. Therefore the documents should be prepared
in \LaTeX{} form, but a very simple version. 


\subsection{Getting the source}
\paragraph{Note:} The repository has recently been changed to use SVN instead of CVS, if any 
references to CVS remain in the following document, please replace with the appropriate SVN commands.
The source is stored using SVN. The repository is at 

\begin{verbatim}
http://xe01/svn/docs
\end{verbatim}
and the package is called 

\begin{verbatim}
docs
\end{verbatim}
so the command

\begin{verbatim}
svn co http://xe01/svn/docs/trunk mycopyofdocs

\end{verbatim}
would place all the current versions of the files into the directory
\textbf{mycopyofdocs}.  An example LyX document, \textbf{BlankDoc.lyx},
and some utility shell scripts are included in the package.

The true URL of the current document source  (automatically updated) is:
\verb$URL: http://xe01/svn/docs/trunk/PreparingDocs.tex $

This information should appear at the foot of each document.

\subsection{Features to use}

Each section gets included into the master document, so the section
should not have a preamble, and should not have \textbackslash{}begin\{document\}
and \textbackslash{}end\{document\} commands.

The section should begin with the special section header command

\begin{verbatim}
\tophead{title text}
\end{verbatim}
Subsections and sub-sub sections use the commands:

\begin{verbatim}
\subsection{heading text}
\subsubsection{subheading text\}
\end{verbatim}

Included computer code uses the \textit{verbatim} environment


{\ttfamily\textbackslash{}begin\{verbatim\}

Anything typed here will be printed exactly,

no matter how many \verb={*}\&\{`\#\%= special characters it has. 

\textbackslash{}end\{verbatim\}
}

For version tracking, it is helpful to include the lines

{\ttfamily
	\verb|\vfill{}|

	\textbackslash{}verb\$Revision:\$

	\textbackslash{}verb\$Date:\$\textbackslash{}par\{\}

	\textbackslash{}verb\$URL:\$

}

at the end of the file. This will be changed by SVN to include the
actual revision and date of the document, making it easy to spot when
someone is using an out-of-date version.


\subsection{How to prepare the file}

You can use a variety of methods to edit and prepare the doucument.
I can suggest four:

\begin{itemize}
%\item Use a \LaTeX{} front-end such as \LyX{} or Kile.
\item Use a \LaTeX{} front-end such as Kile.
\item Use a text editor
%\item Use Microsoft Word and convert with wvCleanLatex
\end{itemize}
Each has its advantages and disadvantages. 

\paragraph{Kile  Front end }
%At present, the most recent version is only available on Mig. This
%program allows all features of \LaTeX{} to be used properly including
%\textit{verbatim} environments and code. It does not run on Windows. It
%is a KDE program.
Kile includes the function for previewing a sub-document:
\begin{enumerate}
   \item Open the \textit{documentation.tex} file
   \item Select \textbf{Settings | Define current document as master document}
   \item Open the file for one of the sections
   \item Select \textbf{Build | Quick Preview | Subdoucment }
\end{enumerate}

%\paragraph{\LyX{} Front end }
%
%Using \LyX{} will require that you export the project as \LaTeX{},
%then use a script to remove the beginning and end material from the file. The script 
%\begin{verbatim}
%unlyxdoc
%\end{verbatim}
%is included for this purpose.
%
%Alternately, you may manually delete all the lines up to
%and including \begin{document}, remove
%the \textbackslash{}end\{document\} at the end, and change
%\textbackslash{}section to \textbackslash{}tophead for the section title,
%so that it gets printed at the top of each page in the section.
%
%\begin{itemize}
%\item You should use the \textbf{Section} format for the main section title,
%the script will change it to \textbackslash{}tophead\{ ... \} or you can do this manually after exporting.
%
%\item Use \textbf{Subsection, Subsubsection,} and \textbf{Paragraph} formats
%for internal sections
%\item You may use the \textbf{verbatim} environment instead of the \LaTeX{} \textit{verbatim} for code listings.
%
%I think it should work but it is not really a verbatim listing. If
%it does not work for a particular case, you may need to manually change
%\textbackslash{}begin\{verbatim\} ...\textbackslash{}end\{verbatim\}
%to \textbackslash{}begin\{verbatim\} ... \textbackslash{}end\{verbatim\}
%and edit the listing a bit. Hopefully future versions of \LyX{} will
%incorporate the verbatim environment.
%
%\item \textbf{Itemize} and \textbf{Enumerate} for numbered/bulleted lists.
%\end{itemize}

\paragraph{Text editor}

Using a text editor requires that you enter the \LaTeX{} commands
yourself. As the commands used should be confined to the heading and
section commands, and lists or numbered lists, this is not so bad. Use 
\begin{verbatim}
\tophead{my heading}
\end{verbatim}
to set the main section heading instead of \textbackslash{}section\{\}. This sets the text at the top of each page, and 
is used as the marker to split the html and pdf files into sections.

%\paragraph{Word conversion}
%
%The program \textbf{wvCleanLatex} usually produces \LaTeX{} that results
%in a document with the appearance of the Word document. However, the
%logical structure is not preserved. Headings are just done in boldface
%instead of Section, so they are not incorporated into the table of
%contents. To properly integrate the document, a fair bit of manual
%editing is required. However, this still may be easier than editing
%the doucment from scratch especially if a Word document already exists.
%

\subsection{How to Create the Document}

Once you have the \LaTeX{} file for the section, you should test the
appearance of your modified \LaTeX{} file when used with the common
header. The instructions below assume that the dvi and pdf viewers
availabel are \textbf{xdvi} and \textbf{xpdf}, however many other
viewers are around. On a windows system Acrobat reader may be used
for pdf files. A good dvi viewer called \textbf{yap} is available
in the Mik\TeX{} distribution. Using an account on \textit{mig} may be easiest since 
\LyX{}, Kile, and the other tools are already installed and working.

\subsubsection{Previewing the section}

The script \textbf{testnewdoc} is provided for testing the appearance
of a new document section before integrating it with the others. If you
have created a document called \textbf{UsingMyProgram.tex}, 
call the script:


\begin{verbatim}
./testnewdoc~UsingMyProgram
\end{verbatim}
This will create a temporary version in which the headers have been
included, and run \LaTeX{} to produce a .dvi output file. The file has the
extra suffix \textit{tmp.} The file may be viewed with the \textbf{xdvi} program:

\begin{verbatim}
xdvi UsingMyProgramtmp.dvi
\end{verbatim}

\paragraph{Note:} If you use Kile to prepare the section, you can use
the \textbf{Build | Quick Preview | Subdocument} command as described
above. Some of preceding steps may not be necessary.

\subsubsection{Incorporating the new section in the master document}
If the preview works as desired, the new section may be inserted in the master
documentation file, \textbf{documentation.tex.} Insert the line

\begin{verbatim}
\include{UsingMyProgram.tex}
\end{verbatim}
into the appropriate place in the list of included files. Then test
your section with the script \textbf{makedoc:}

\begin{verbatim}
./makedoc UsingMyProgram
\end{verbatim}
The difference is that this tests your file in combination with all
the other sections, then prints out only your section. View using
xpdf:

\begin{verbatim}
xpdf UsingMyProgram.pdf
\end{verbatim}
If this is successful, you should checkin your documentation section

\subsubsection{Adding the new section to the repository}

The new section may be added to the repository when it is ready using the commands:
\begin{verbatim}
svn add UsingMyProgram.tex
svn ci 
\end{verbatim}

In order to enable `keyword substitution' in svn, the \textit{keyword} properties must be set for the file
\begin{verbatim}
svn propset svn:keywords "Url Revision Date Id" UsingMyProgram.tex
\end{verbatim}


The section will be added to the html and pdf on the webserver when
the automated process runs, each day at 2 AM.
\paragraph{Root users} can manually update the webpage on the web server 
using the script sbin/make\_docs:
\begin{verbatim}
$ su -
password: #####
# sbin/make_docs
# exit
$
\end{verbatim}
This script updates the working copy from the repository, then builds 
html and pdf versions and copies them to the web server's directory.


\vfill{}
\verb$Revision: 109 $
\verb$Date: 2007-11-30 12:22:27 +0000 (Fri, 30 Nov 2007) $


\verb$URL: http://xe01/svn/docs/trunk/PreparingDocs.tex $

